Confound and control in language experiments

### 2016-08-02 poster-snl2016.tex
frankfurt logos

\begin{block}{Try the app!}
\centering
\includegraphics[width=0.6\textwidth]{shinyapps-url.eps}
%
%http://rpubs.com/palday/statfail
\end{block}

\begin{block}{Read the preprint!}
\centering
\includegraphics[width=0.6\textwidth]{arxiv-url.eps}
%

@@

\begin{block}{}
\begin{tabular}{c c c}
\includegraphics[width=.55\linewidth]{logo_unisa_RGB-blue.png} &   \includegraphics[width=.4\linewidth]{cnl-color.eps} & \\
\end{tabular}

>>>>

\begin{block}{Try the app!}
\centering
\includegraphics[width=0.55\textwidth]{shinyapps-url.eps}
%
%http://rpubs.com/palday/statfail
\end{block}

\begin{block}{Read the preprint!}
\centering
\includegraphics[width=0.55\textwidth]{arxiv-url.eps}
%

@@

\begin{block}{}
\begin{tabular}{c c }
\includegraphics[width=.55\linewidth]{logo_unisa_RGB-blue.png} &   \includegraphics[width=.3\linewidth]{cnl-color.eps}  \\
\includegraphics[width=.4\linewidth]{logo_frankfurt_square.png} & \includegraphics[width=.4\linewidth]{logo_fiebach_lab.png} \\
\end{tabular}
